---
title: "Improved blblm package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{JC-blblm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Summary

blblm package is for doing linear model computation with *bag of little bootstraps* (BLB). Bag of little bootstrap is a procedure that incorporates bootstrap and resampling to prodce a computationally efficient, yet robust way of estimation.

# blblm Package

To download and install blblm package with single R command:
```{r}
devtools::install_github("ucdavis-sta141c-sq-2020/blblm")
```

To load the package and examine other packages attached when you use blblm:
```{r setup}
library(blblm)
```

# Design Principles

The improved package aims to increase the efficiency of linear model computation. On top of the original version of blblm package, this version enables user-specified parallel computing, using input of multiple files and the choice of logistic regression.

## Parallelization

The function is written in the following:

```{r}
blblm_par_sing <- function(formula, data, m, B, nCluster=1){
  data_list <- split_data(data, m)
  suppressWarnings(plan(multiprocess, workers = nCluster))
  estimates <- future_map(data_list,
                         ~lm_each_subsample(formula = formula, data = ., n = nrow(data), B = B))
  res <- list(estimates = estimates, formula = formula)
  class(res) <- "blblm"
  invisible(res)
}
```

plan(multiprocess, workers = nCluster) enables parallelization, which is accompanied by future_map from library(furrr) for the computing. User inputs the regression x and y terms, the data source, number of data splits, number of bootstraps and desired number of clusters to use as the parameters.

```{r, include=FALSE}
library(furrr)
```


```{r, eval=FALSE}
fit <- blblm_par_sing(mpg ~ wt * hp, data = mtcars, m=3, B=100, nCluster = 4)
coef(fit)
```

## Multiple files capable

Similar to the implementation of parallel computing version of blblm, this version can be used when user wants to use a list of specified files.

```{r}
blblm_par <- function(formula, file_names, m, B, nCluster){
  suppressWarnings(plan(multiprocess, workers = nCluster))
  data <- file_names %>% future_map(.,~read_csv(col_types = cols()))
  data_list <- split_data(data, m)
  estimates <- future_map(data_list,
                            ~lm_each_subsample(formula = formula, data = ., n = nrow(data), B = B))
  res <- list(estimates = estimates, formula = formula)
  class(res) <- "blblm"
  invisible(res)
}
```

On top of the previous version blblm_par_sing, this version has the data input field as file_names, which takes a list of filenames for data extraction.

## Logistic Regression

A replicate of blblm in logistic regression. Input parameters stay the same with the previous version, and take a list of file names as data input

```{r}
blblm_lr <- function(formula, data, m, B, nCluster){
  suppressWarnings(plan(multiprocess, workers = nCluster))
  data <- file_names %>% future_map(.,~read_csv(col_types = cols()))
  data_list <- split_data(data, m)
  estimates <- future_map(data_list,
                          ~lr_each_subsample(formula = formula, data = ., n = nrow(data), B = B))
  res <- list(estimates = estimates, formula = formula)
  class(res) <- "blblm"
  invisible(res)
}
```






